Our peculiar motion across the Universe

### 2019-06-25 paper/main.tex
peculiar velocity

\begin{figure*}
\begin{center}
  \includegraphics[width=0.9\textwidth]{cumulative_probability_18.pdf}
\end{center}
\caption{Distributions of peculiar velocities for MW type halos
  (individual, paired and observed). 
  Left panel shows the estimated probability density.
  The right panel shows the cumulative probability density.
  Paired halos have a slightly lower peculiar velocity than isolated
  halos.
  The observed peculiar velocity ($v_p=627\pm22$ km s$^{-1}$) shown as
  the vertical shaded stripe, is always located on the high velocity
  tail of simulations.}
\label{fig:proba}
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.4\textwidth]{cumulative_alignment_06.pdf}
\end{center}
\caption{Cumulative probability for the dot product between the unit
  vector joining the two dominan halos in the pair and the peculiar
  velocity of the less massive halo.
  Continous line: results for all pairs; dashed line: pairs where the
  less massive halo moves with a pecular velocity larger than
  $v_p=627\pm22$ km s$^{-1}$.}
\label{fig:alignment}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
  \includegraphics[width=0.9\textwidth]{cumulative_probability_18.pdf}
\end{center}
\caption{Distributions of peculiar velocities for MW type halos
  (individual, paired and observed). 
  Left panel shows the estimated probability density.
  The right panel shows the cumulative probability density.
  Paired halos have a slightly lower peculiar velocity than isolated
  halos.
  The observed peculiar velocity ($v_p=627\pm22$ km s$^{-1}$) shown as
  the vertical shaded stripe, is always located on the high velocity
  tail of simulations.
  Halos in isolated pairs tend to have lower peculiar velocities than
  the general sample of individual halos.}
\label{fig:proba}
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.4\textwidth]{cumulative_alignment_06.pdf}
\end{center}
\caption{Cumulative probability for the dot product between the unit
  vector joining the two halos in the pair and the peculiar
  velocity of the less massive halo.
  Continous line: results for all pairs; dashed line: pairs where the
  less massive halo moves with a pecular velocity larger than
  $v_p=627\pm22$ km s$^{-1}$.
  The vertical stripe shows the values for the MW and M31.
  Halos with high peculiar velocities tend to be aligned in the
  direction towards its partner.}
\label{fig:alignment}
\end{figure*}
